%% See https://github.com/xdanaux/moderncv/blob/master/manual/moderncv_userguide.v2.pdf for information or https://github.com/xdanaux/moderncv/blob/master/examples/template.tex
\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking} % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[utf8]{inputenc} 
\usepackage[scale=0.9]{geometry} % adjust the page margins
%\setlength{\hintscolumnwidth}{3cm} % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}\ % force the width allocated to your name and avoid line breaks.

\firstname{Marlon}
\familyname{Guimarães}
\address{Brasília, Brazil} % optional
\email{marlonciriatico@gmail.com} % optional
\phone[fax]{+55~(21)~99768 8899} % optional
\social[linkedin]{marlonciriatico} 
\social[github]{marlonguimaraes}

\begin{document}
\makecvtitle

\section{Education}
\cventry{March 2014 -- December 2019}{Bachelor in Software Engineering}{University of Brasilia}{Brasília - Brazil}{}{}
\cventry{October 2013 -- November 2013}{Innovation and Immersion in American Culture and History}{Georgetown University}{Washington, DC - United States}{}{}  % arguments 3 to 6 can be left empty

\section{Skills}
\cvitem{Programming languages}{TypeScript, JavaScript, Python, C\#, Golang (Go), Java, C++, C}
\cvitem{Technologies}{React, GraphQL, Node.js, REST, Unity 3D, Git, Bash, Docker, Next.js, PostgreSQL, Redis, CSS}

\section{Professional Experience}

\cventry{March 2020 -- Present}{Software Engineer - VTEX App Store Team}{VTEX}{Rio de Janeiro}{}{VTEX is an e-commerce platform with more than 2900 company clients, operating in 42 countries. Worked on the product VTEX App Store, an e-commerce that sells extensions for VTEX stores.\newline
\begin{itemize}%
\item Developed the Checkout page with user authentication and authorization (React, GraphQL, TypeScript, Tachyons);
\item Built the subscription service that charge users monthly with an on-demand price model  (Node.js, REST, Jest for unit tests);
\item Implemented the product submission flow where vendors send software packages to be sold in the marketplace (Node.js, npm, oclif).\newline
\end{itemize}}

\cventry{December 2018 -- March 2019}{Game Development Engineer Intern - Sniper 3D Team}{Wildlife Studios}{São Paulo}{}{Sniper 3D is a mobile game played by more than 15 million users worldwide.\newline
\begin{itemize}%
\item Developed PvP rankings for world, country and city divisions based on players IP addresses (Go, PostgreSQL, Redis, Docker);
\item Improved the map selection UI and player progress feedback across the game campaign (Unity 3D, C\#);
\item Built AB tests to quantify how users interacted with new features added in the game (Unity 3D, C\#).\newline
\end{itemize}}
    
\cventry{January 2018 -- December 2018}{Software Engineer Intern - Salic ML Team}{LAPPIS}{Brasília}{}{Salic ML is a team that applied data science to the process of reviewing cultural projects submitted to a government system.\newline
\begin{itemize}%
\item Developed scripts that parsed and prepared data from a database to be used in models and analysis (Python, pandas, numpy);
\item Built Jupyter Notebooks to get graphical and statistical insights from data (Jupyter Notebook, matplotlib);
\item Implemented models to detect novelty in the data using Local Outlier Factor and Gaussian distribution (scikit-learn).
\end{itemize}}

\section{Personal projects}
\cventry{February 2021 -- Present}{}{YouTube Instant Autoplay}{}{}{Google Chrome browser extension that improves the YouTube viewer experience. There are now users from more than 15 countries.\newline
\begin{itemize}%
\item Deployed on \href{https://chrome.google.com/webstore/detail/youtube-instant-autoplay/daaddadfbkngjhmjgcmmbeomechfoacb}{\color{blue}{\underline{Chrome Web Store}}};
\item Built a script that reads page changes events and interact with the YouTube player (Google Chrome API, JavaScript, HTML).
\end{itemize}}

\pagebreak

\cventry{November 2020 -- Present}{}{Discover Daily}{}{}{Discover Daily is a website where users can have daily personalized music recommendations based on user Spotify's history.\newline
\begin{itemize}%
\item Implemented User Authentication with OAuth 2.0 and Spotify (OAuth 2, Spotify API);
\item Developed Responsive front-end and Server Side Rendering (React, Tachyons CSS, Next.js).
\item Implemented GraphQL server for providing client with music recommendations (GraphQL, TypeScript).\newline
\end{itemize}}

\cventry{December 2015 -- Present}{}{competitive\_programming}{}{}{Open source \href{https://github.com/marlonguimaraes/competitive_programming}{\color{blue}{\underline{repository}}} with implementations of algorithms, data structures and techniques used in programming competitions.\newline
\begin{itemize}%
\item Implemented algorithms for topics like Data Structures, Graph Theory, Math, Dynamic programming and String-matching.
\end{itemize}}

\section{Programming competitions}
\cvitem{ACM ICPC Brazilian First Phase (State)}{Competed in 2015 (9th place), 2016 (1st place), and 2017 (1st place).}
\cvitem{ACM ICPC Brazilian Finals (National)}{Competed in 2016 (14th place) and 2017 (13th place).}

\section{University projects}

\cventry{March 2019 -- December 2019}{GoDash}{Bachelor final project}{}{}{GoDash is a 2D multiplayer shooter game developed during my bachelor final project.\newline
\begin{itemize}%
\item Implemented multiplayer networking solution using Remote Procedure Calls through UNet API (C\#, Unity 3D, UNet);
\item Built bots with artificial intelligence that play real time matches against human players. (C\#, UNet, pathfinding algorithms).\newline
\end{itemize}}

\cventry{March 2018 -- July 2018}{Cardinals}{Software Product Engineering course}{}{}{Website that provides data analysis for GitHub repositories.\newline
\begin{itemize}%
\item Implemented the DevOps continuous integration and delivery (CI/CD) with automated tests, code analysis and deploys on Heroku (Python, Docker, docker-compose, pytest, Flake8);
\item Front-end for data visualization about repository information (Python, matplotlib, django);
\item Built user authorization allowing GitHub API requests (Python, OAuth 2.0).
\end{itemize}}

\end{document}